### 2023-09-29 manuscript.tex
adjust text with better layer [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/d5d46176b84f0009a2f0c2c96017236ef1b2bc9f.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/d5d46176b84f0009a2f0c2c96017236ef1b2bc9f/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/6358233770

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/805720c4c9ab45e392cf7c613f4c525f9a8c0b2c/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/805720c4c9ab45e392cf7c613f4c525f9a8c0b2c}{MMV-Lab/im2im-paper@805720c}
on September 29, 2023.

@@

In this paper, we introduce \emph{MMV\_Im2Im} an open-source microscopy machine vision (MMV) toolbox for image-to-image transformation and demonstrate its applications in over 10 biomedical tasks of various types by performing more than 30 experiments. Currently, \emph{MMV\_Im2Im} supports 2D\textasciitilde5D microscopy images for supervised image-to-image translation (e.g., labelfree determination {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, imaging modality transformation {[}\protect\hyperlink{ref-WwenuBHa}{5},\protect\hyperlink{ref-UEBDZ3tI}{8}{]}), supervised image restoration {[}\protect\hyperlink{ref-wcCVn8av}{6}{]}, supervised semantic segmentation {[}\protect\hyperlink{ref-TutLhFSz}{9}{]}, supervised instance segmentation {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]}, unsupervised semantic segmentation {[}\protect\hyperlink{ref-RuFP3CS3}{12}{]}, unsupervised image to image translation and synthetization {[}\protect\hyperlink{ref-6wtIu4QY}{13}{]}. The toolbox will continuously grow with more and more methods, such as self-supervised learning based methods, ideally also with contributions from the open-source community.

@@

Our package \emph{MMV\_Im2Im} employs pytorch-lightning {[}\protect\hyperlink{ref-YbvSvdyB}{14}{]} as the core in the backend, which offers numerous benefits, such as readability, flexibility, simplicity and reusability. First of all, have you ever had the moment when you wanted to extend someone's open-source code to suit your special ML needs, but found it so difficult to figure out where and how to extend, especially for complex methods? Or, have you ever encountered the situation where you want to compare the methods and code from two different papers, even solving the same problem, e.g.~semantic segmentation, but not quite easy to grasp quickly since the two repositories are implemented in very different ways? It is not rare that even different researchers from the same group may implement similar methods in very different manners. This is not only a barrier for other people to learn and re-use the open-source code, but also poses challenges for developers in maintenance, further development, and interoperability among different packages. We follow the pytorch-lightning framework and carefully design a universal boilerplate for image-to-image transformation for biomedical applications, where the implementation of all the methods share the same modularized code structure. For all PyTorch users, this greatly lowers the learning curve for people to read and understand the code, and makes implementing new methods or extending existing methods simple and fast, at least from an engineering perspective.

@@

\emph{2D Labelfree:} We started with a simple problem using 2D images from the HeLa ``Kyoto'' cells dataset {[}\protect\hyperlink{ref-xv2VIyRP}{23}{]}. For all images, we took the brightfield channel and the mCherry-H2B channel out of the multi-channel timelapse movies. 2D images were acquired at 20x with 0.8 N.A. and then downscaled by 4 (pixel size: 0.299 nm x 0.299 nm). Example predictions can be found in Figure \ref{fig:labelfree_comparison}-A. We compared a basic UNet model {[}\protect\hyperlink{ref-TutLhFSz}{9}{]} and a 2D version of the fnet model in {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. The fnet model achieved slightly more accurate predictions than the basic UNet, this can be seen in Figure \ref{fig:labelfree_comparison}-A.

@@

We conducted three groups of comparisons (see results in Figure \ref{fig:labelfree_comparison}-B). First, we compared three different image normalization methods for 3D images: percentile normalization, standard normalization, center normalization {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. Percentile normalization refers to cutting the intensity out of the range of {[}0.5, 99.5{]} percentile of the image intensity and then rescale the values to the range of {[}-1, 1{]}, while the standard normalization is simply subtracting mean intensity and then divided by the standard deviation of all pixel intensities. Center normalization is similar to standard normalization, but the statistics are calculated only around the center along the Z-axis {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. One could easily test different percentiles or rescaling to {[}0, 1{]} instead of {[}-1, 1{]}. Qualitatively, we found center normalization slightly more accurate and more robust than the other two (see first row of Figure \ref{fig:labelfree}-B).

@@

Finally, we showed the comparison between three different types of models, an FCN-type model (i.e., fnet), a pix2pix-type model, and a cycleGAN-type model. For fair comparison, we used fnet as the same backbone for all three types of models. In theory, the pix2pix-type model can be trained in two different ways: from scratch or initializing the generator with a pre-trained fnet (trained as FCN). Examples of the comparison results were shown in the last two rows in Figure \ref{fig:labelfree}-B. Visually, it is evident that the additional adversarial components (i.e., the discriminator) could generate images with more realistic appearance than a typical FCN-type model alone, but again, we leave the appropriate quantitative evaluations to users' specific biomedical studies.

From the experiments above, we found that center normalization + pix2pix with fnet as the generator achieved the best overall performance qualitatively. So, we employed the same strategy on all other nuclear structures. At the end, we had four different labelfree models, each predicting one different nuclear structure from 3D brightfield images. As an example of evaluation, we calculated the pearson correlation, the structural similarity and the peak signal to noise ratio on holdout validation sets. The results were summarized in Table \ref{tbl:labelfree_table}. Again, these numbers were merely examples of evaluation, systematic evaluation based on each specific biological problem would be necessary before deployment. Figure \ref{fig:labelfree_all_structures}-A shows the comparison of each predicted structure and its ground truth, while Figure \ref{fig:labelfree_all_structures}-B shows one example of all four different structures predicted from a single unseen brightfield image. This would permit an integrated analysis of four different nuclear components that could hardly be acquired simultaneously in real experiments and real images.

@@

We did a special comparison in this subsection to further illustrate the difference between semantic and instance segmentations. We took the 3D fibrillarin dataset from {[}\protect\hyperlink{ref-5sGcmDuy}{24}{]}. There are multiple channels in each 3D image, including DNA dye, membrane dye, and the structure channel (i.e., fibrillarin in this case). The original fibrillarin segmentation released with the dataset is a semantic segmentation (0=background, 1=fibrillarin). With the additional cell segmentation available in the dataset, we can know which groups of segmented fibrillarin belong to the same cell. Then, we can convert the original 3D fibrillarin semantic segmentation ground truth into 3D instance segmentation ground truth (fibrillarin pixels belonging to the same cell are grouped as a unique instance). Sample images and results are shown in Figure \ref{fig:3dseg}. We can observe that the semantic segmentation model is able to achieve good accuracy in determining pixels from the fibrillarin signals (F1 = 0.958 ± 0.008). Meanwhile, the instance segmentation can group them properly (average precision at 50 = 0.795) so that fibrillarin masks from the same cell are successfully identified as unique instances, even without referring to the cell membrane channel or cell segmentation results. This is not a simple grouping step based on distance, since the fibrillarin signals from tightly touching nuclei may exist very close to each other.

\begin{figure}
\hypertarget{fig:3dseg}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/semantic_seg3d_justin.png}
\caption{Comparing 3D semantic segmentation and 3D instance segmentation results on confocal microscopy images of fibrillarin (showing a middle Z-slice of a 3D stack). Shown are the raw image, the prediction of the instance segmentation, and for both segmentations a mask that gives an overview of true positive, false negative, and false positive pixels.}\label{fig:3dseg}
}
\end{figure}

@@

For 3D demonstration, we use 3D H2B images with two different types of input masks. First, we attempted to generate synthetic images from a coarse mask (i.e., only the overall shape of the nucleus, available as nuclear segmentation from the dataset) with both supervised training and unsupervised training. The unsupervised model in \emph{MMV\_Im2Im} uses the CycleGAN-based approaches. So, the unsupervised training is actually already done within the unsupervised segmentation experiments. In other words, the unsupervised model works in a bi-directional way, from real microscopy images to binary masks, and also from binary masks to simulated microscopy images. Here, we just do the inference in a different direction (from binary to simulated microscopy) using the model trained in the unsupervised segmentation section. The results are shown in Figure \ref{fig:synthetic}-B (row 1). The unsupervised synthesization can mostly ``paint'' the mask with homogeneous grayscale intensity, while the supervised model can simulate the textures to some extent. For a relatively large mask, it could be challenging for a model to fill in sufficient details to simulate real microscopy images (might be improved with diffusion-based models, see Discussions).

@@

In this example, we presented an image denoising demonstration with sample data from {[}\protect\hyperlink{ref-12G712Zky}{41}{]}. The goal was to increase the quality of low signal-to-noise ratio (SNR) images of nucleus-stained flatworms (Schmidtea mediterranea, planaria) and lightsheet images of Tribolium castaneum (red flour beetle) embryos. The models were trained with paired data acquired with low and high laser intensity on fixed samples, and then applied on live imaging data. For the nucleus-stained flatworm data (a test set of 20 images are available), the model achieved pearson correlation of 0.392 ± 0.065, while the pearson correlation between the noisy raw and ground truth images was 0.065 ± 0.057. For the red flour beetle dataset, the model has improved the pearson correlation from 0.219 ± 0.045 to 0.444 ± 0.077 (6 images). Based on this and the results in Figure \ref{fig:denoising}, it can be observed that the low SNR images can be greatly improved. Systematic quantitative evaluations would be necessary to confirm the biological validity, but beyond the scope of this paper.

@@

Another important application of image-to-image transformation is imaging modality transformation {[}\protect\hyperlink{ref-UEBDZ3tI}{8}{]}, usually from one ``cheaper'' modality with lower resolution (e.g., with larger field-of-view, easier to acquire and scale up) to another modality with higher resolution but expensive to obtain. Such models will permit a new way in assay development strategy to take advantage of all the benefits of the cheaper modality with lower resolution and still be able to enhance the resolution computationally post hoc. To demonstrate the application of \emph{MMV\_Im2Im} in this scenario, we took an example dataset with paired 3D confocal and Stimulated Emission Depletion (STED) images of two different cellular structures, microtubule and nuclear pore {[}\protect\hyperlink{ref-UEBDZ3tI}{8}{]}. Sample results were summarized in Figure \ref{fig:modality_np} and Figure \ref{fig:modality_mt}. The corresponding error plots show pixel-based absolute differences between ground truth and prediction. Intensities were normalized to the interval from -1 to 1 for training, with intensity limits restricted to the 0.01-percentile and 99.99-percentile values of the intensity distribution.

\begin{figure}
\hypertarget{fig:modality_mt}{%
\centering
\includegraphics[width=0.65\textwidth,height=0.7\textheight]{images/mt_manuscript.png}
\caption{Example results of confocal-to-STED modality transformation of microtubule in three consecutive z-slices. From top to bottom: raw confocal images, reference STED images, predicted images, error plots. For the error plots, the ground truth images were normalized as described in the main text. The contrast of grayscale images was adjusted using ImageJ's autoscale.}\label{fig:modality_mt}
}
\end{figure}

For microtubule, the model achieved pearson correlation of 0.786 ± 0.020 and a peak signal to noise ratio of 21.201 ± 0.586, while for nuclear pore complex, the pearson correlation was 0.744 ± 0.025 and the peak signal to noise ratio was 22.939 ± 1.896. Considering a pearson correlation of 0.699 ± 0.030 and a peak signal to noise ratio of 18.847 ± 0.649 for the microtubule dataset and a pearson correlation of 0.656 ± 0.033 and a peak signal to noise ratio of 20.352 ± 1.009 of the lower resolution raw images with the higher resolution ground truth, this approach improved data quality. Also, visual inspection can confirm the effectiveness of the models. Again, it would be necessary to conduct further quantitative evaluation to ensure the validity of users' specific problems.

\begin{figure}
\hypertarget{fig:modality_np}{%
\centering
\includegraphics[width=0.65\textwidth,height=0.7\textheight]{images/np_manuscript.png}
\caption{Example results of confocal-to-STED modality transformation nuclear pore in three consecutive z-slices. From top to bottom: raw confocal images, reference STED images, predicted images, error plots. For the error plots, the ground truth images were normalized as described in the main text. The contrast of grayscale images were adjusted using ImageJ's autoscale.}\label{fig:modality_np}
}
\end{figure}

@@

From all experiments above (37 in total), we want to demonstrate the great flexibility of \emph{MMV\_Im2Im} and not to optimize every task in details.Presenting all detailed configurations in these 37 experiments in the manuscript could lead to more confusion than clarity. To this end, we give a high-level overview of the key information of each task in Table \{tbl:framework\_overview\}, hoping to serve as a valuable starting point for researchers to optimize their DL-based image-to-image transformation using \emph{MMV\_Im2Im}. The full configuration details are available in human-readable formats in our GitHub repository (https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs).

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/d5d46176b84f0009a2f0c2c96017236ef1b2bc9f/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/d5d46176b84f0009a2f0c2c96017236ef1b2bc9f}{MMV-Lab/im2im-paper@d5d4617}
on September 29, 2023.

@@

In this paper, we introduce \emph{MMV\_Im2Im} an open-source microscopy machine vision (MMV) toolbox for image-to-image transformation and demonstrate its applications in over 10 biomedical tasks of various types by performing more than 30 experiments. Currently, \emph{MMV\_Im2Im} supports 2D\textasciitilde5D microscopy images for supervised image-to-image translation (e.g., labelfree determination {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}, imaging modality transformation {[}\protect\hyperlink{ref-WwenuBHa}{5},\protect\hyperlink{ref-UEBDZ3tI}{8}{]}), supervised image restoration {[}\protect\hyperlink{ref-wcCVn8av}{6}{]}, supervised semantic segmentation {[}\protect\hyperlink{ref-TutLhFSz}{9}{]}, supervised instance segmentation {[}\protect\hyperlink{ref-K2ugNcVa}{10},\protect\hyperlink{ref-QmYuUQ5K}{11}{]}, unsupervised semantic segmentation {[}\protect\hyperlink{ref-RuFP3CS3}{12}{]}, unsupervised image to image translation and synthetization {[}\protect\hyperlink{ref-6wtIu4QY}{13}{]}. The toolbox will continuously grow with more and more methods, ideally also with contributions from the open-source community.

@@

Our package \emph{MMV\_Im2Im} employs pytorch-lightning {[}\protect\hyperlink{ref-YbvSvdyB}{14}{]} as the core in the backend, which offers numerous benefits, such as readability, flexibility, simplicity and reusability. First of all, have you ever had the moment when you wanted to extend someone's open-source code to suit your special ML needs, but found it so difficult to figure out where and how to extend, especially for complex methods? Or, have you ever encountered the situation where you want to compare the methods and code from two different papers, even solving the same problem, e.g.~semantic segmentation, but not quite easy to grasp quickly since the two repositories are implemented in very different ways? It is not rare that even different researchers from the same group may implement similar methods in very different manners. This is not only a barrier for other people to learn and re-use the open-source code, but also poses challenges for developers in maintenance, further development, and interoperability among different packages. We follow the pytorch-lightning framework and carefully design a universal boilerplate for image-to-image transformation for biomedical applications, where the implementation of all the methods share the same modularized code structure. For all PyTorch users, this greatly lowers the barrier for people to read and understand the code, and makes implementing new methods or extending existing methods simple and fast, at least from an engineering perspective.

@@

\emph{2D Labelfree:} We started with a simple problem using 2D images from the HeLa ``Kyoto'' cells dataset {[}\protect\hyperlink{ref-xv2VIyRP}{23}{]}. For all images, we took the brightfield channel and the mCherry-H2B channel out of the multi-channel timelapse movies. 2D images were acquired at 20x with 0.8 N.A. and then downscaled by 4 (pixel size: 0.299 nm x 0.299 nm). Example predictions can be found in Figure \ref{fig:labelfree_comparison}-A. We compared a basic UNet model {[}\protect\hyperlink{ref-TutLhFSz}{9}{]} and a 2D version of the fnet model in {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. The fnet model achieved slightly more accurate predictions than the basic UNet, as seen in Figure \ref{fig:labelfree_comparison}-A.

@@

We conducted three groups of comparisons (see results in Figure \ref{fig:labelfree_comparison}-B). First, we compared three different image normalization methods for 3D images: percentile normalization, standard normalization, center normalization {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. Percentile normalization refers to cutting the intensity out of the range of {[}0.5, 99.5{]} percentile of the image intensity and then rescale the values to the range of {[}-1, 1{]}, while the standard normalization is simply subtracting mean intensity and then divided by the standard deviation of all pixel intensities. Center normalization is similar to standard normalization, but the statistics are calculated only around the center along the Z-axis {[}\protect\hyperlink{ref-Yq8wZ6hc}{4}{]}. One could easily test different percentiles or rescaling to {[}0, 1{]} instead of {[}-1, 1{]}. Qualitatively, we found center normalization slightly more accurate and more robust than the other two (see first row of Figure \{{[}\protect\hyperlink{ref-labelfree_all_structures}{\textbf{labelfree\_all\_structures?}}{]}\}-B).

@@

Finally, we showed the comparison between three different types of models, an FCN-type model (i.e., fnet), a pix2pix-type model, and a cycleGAN-type model. For fair comparison, we used fnet as the same backbone for all three types of models. In theory, the pix2pix-type model can be trained in two different ways: from scratch or initializing the generator with a pre-trained fnet (trained as FCN). Examples of the comparison results were shown in the last two rows in Figure \{{[}\protect\hyperlink{ref-labelfree_all_structures}{\textbf{labelfree\_all\_structures?}}{]}\}-B. Visually, it is evident that the additional adversarial components (i.e., the discriminator) could generate images with more realistic appearance than a typical FCN-type model alone, but again, we leave appropriate evaluations to users' specific biomedical studies.

From the experiments above, we found that center normalization + pix2pix with fnet as the generator achieved the best overall performance qualitatively. So, we employed the same strategy on all other nuclear structures. At the end, we had four different labelfree models, each predicting one different nuclear structure from 3D brightfield images. As an example of evaluation, we calculated the Pearson correlation, the structural similarity and the peak signal to noise ratio on holdout validation sets. The results were summarized in Table \ref{tbl:labelfree_table}. Again, these numbers were merely examples of evaluation, systematic evaluation based on each specific biological problem would be necessary before deployment. Figure \ref{fig:labelfree_all_structures}-A shows the comparison of each predicted structure and its ground truth, while Figure \ref{fig:labelfree_all_structures}-B shows one example of all four different structures predicted from a single unseen brightfield image. This would permit an integrated analysis of four different nuclear components that could hardly be acquired simultaneously in real experiments and real images.

@@

We did a special comparison in this subsection to further illustrate the difference between semantic and instance segmentations. We took the 3D fibrillarin dataset from {[}\protect\hyperlink{ref-5sGcmDuy}{24}{]}. There are multiple channels in each 3D image, including DNA dye, membrane dye, and the structure channel (i.e., fibrillarin). The original fibrillarin segmentation released with the dataset is binary semantic segmentation. With additional cell segmentations available in the dataset, we can know which groups of segmented fibrillarin belong to the same cell. Then, we can convert the semantic segmentation into 3D instance segmentation ground truth (fibrillarin pixels belonging to the same cell are grouped as a unique instance). Sample images and results are shown in Figure \ref{fig:3dseg}. We can observe that the semantic segmentation model is able to achieve good accuracy in determining pixels from the fibrillarin signals (F1 = 0.958 ± 0.008). Meanwhile, the instance segmentation can group them properly (average precision at 50 = 0.795) so that fibrillarin masks from the same cell are successfully identified as unique instances, even without referring to cell segmentation results. This is not a simple distance-based grouping, since the fibrillarin signals from tightly touching nuclei may exist close to each other.

\begin{figure}
\hypertarget{fig:3dseg}{%
\centering
\includegraphics[width=0.75\textwidth,height=\textheight]{images/semantic_seg3d_justin.png}
\caption{Comparing 3D semantic segmentation and 3D instance segmentation results on confocal microscopy images of fibrillarin (showing a middle Z-slice of a 3D stack), showing true positive, false negative, and false positive pixels.}\label{fig:3dseg}
}
\end{figure}

@@

For 3D demonstration, we use 3D H2B images with two different types of input masks. First, we attempted to generate synthetic images from a coarse mask (i.e., only the overall shape of the nucleus, available as nuclear segmentation from the dataset) with both supervised training and unsupervised training (CycleGAN-based). The unsupervised training is actually already done within the unsupervised segmentation experiments. In other words, the unsupervised model works in a bi-directional way, from real microscopy images to binary masks, and also from binary masks to simulated microscopy images. Here, we just do the inference from binary to simulated microscopy using the model trained in the unsupervised segmentation section. The results are shown in Figure \ref{fig:synthetic}-B (row 1). The unsupervised synthesization can mostly ``paint'' the mask with homogeneous grayscale intensity, while the supervised model can simulate the textures to some extent. For a relatively large mask, it could be challenging for a model to fill in sufficient details to simulate real microscopy images.

@@

In this example, we presented an image denoising demonstration with sample data from {[}\protect\hyperlink{ref-12G712Zky}{41}{]}. The goal was to increase the quality of low signal-to-noise ratio (SNR) images of nucleus-stained flatworms (Schmidtea mediterranea, planaria) and lightsheet images of Tribolium castaneum (red flour beetle) embryos. The models were trained with paired data acquired with low and high laser intensity on fixed samples, and then applied on live imaging data. For the nucleus-stained flatworm data (a test set of 20 images are available), the model achieved Pearson correlation of 0.392 ± 0.065, while the Pearson correlation between the noisy raw and ground truth images was 0.065 ± 0.057. For the red flour beetle dataset, the model has improved the Pearson correlation from 0.219 ± 0.045 to 0.444 ± 0.077 (6 images). Based on this and the results in Figure \ref{fig:denoising}, it can be observed that the low SNR images can be greatly improved. Systematic quantitative evaluations would be necessary to confirm the biological validity, but beyond the scope of this paper.

@@

Another important application of image-to-image transformation is imaging modality transformation {[}\protect\hyperlink{ref-UEBDZ3tI}{8}{]}, usually from one ``cheaper'' modality with lower resolution (e.g., with larger field-of-view, easier to acquire) to another modality with higher resolution but expensive to obtain. Such models will permit a new way in assay development strategy to take advantage of all the benefits of the cheaper modality and still be able to enhance the resolution computationally post hoc. To demonstrate the application of \emph{MMV\_Im2Im} in this scenario, we took an example dataset with paired 3D confocal and Stimulated Emission Depletion (STED) images of two different cellular structures, microtubule and nuclear pore {[}\protect\hyperlink{ref-UEBDZ3tI}{8}{]}. Sample results were summarized in Figure \ref{fig:modality_np} and Figure \ref{fig:modality_mt}. The corresponding error plots show pixel-based absolute differences between ground truth and prediction. Intensities were normalized from 0.01 and 99.99 percentile to {[}-1, 1{]} for training.

\begin{figure}
\hypertarget{fig:modality_mt}{%
\centering
\includegraphics[width=0.65\textwidth,height=0.7\textheight]{images/mt_manuscript.png}
\caption{Example results of confocal-to-STED modality transformation of microtubule in three consecutive z-slices. From top to bottom: raw images, reference STED images, predicted images, error plots. For the error plots, the ground truth images were normalized as described in the main text. The contrast of grayscale images was adjusted using ImageJ's autoscale.}\label{fig:modality_mt}
}
\end{figure}

For microtubule, the model achieved Pearson correlation of 0.786 ± 0.020 and a peak signal to noise ratio of 21.201 ± 0.586, while for nuclear pore complex, the Pearson correlation was 0.744 ± 0.025 and the peak signal to noise ratio was 22.939 ± 1.896. Considering a Pearson correlation of 0.699 ± 0.030 and a peak signal to noise ratio of 18.847 ± 0.649 for the microtubule dataset and a Pearson correlation of 0.656 ± 0.033 and a peak signal to noise ratio of 20.352 ± 1.009 of the lower resolution raw images with the higher resolution ground truth, this approach improved data quality. Also, visual inspection can confirm the effectiveness of the models. Again, it would be necessary to conduct further quantitative evaluation to ensure the validity on users' specific problems.

\begin{figure}
\hypertarget{fig:modality_np}{%
\centering
\includegraphics[width=0.65\textwidth,height=0.7\textheight]{images/np_manuscript.png}
\caption{Example results of confocal-to-STED modality transformation nuclear pore in three consecutive z-slices. From top to bottom: raw images, reference STED images, predicted images, error plots. For the error plots, the ground truth images were normalized as described in the main text. The contrast of grayscale images were adjusted using ImageJ's autoscale.}\label{fig:modality_np}
}
\end{figure}

@@

From all experiments above (37 in total), we want to demonstrate the great flexibility of \emph{MMV\_Im2Im} and not to optimize every task in details. Presenting all detailed configurations in these 37 experiments in the manuscript could lead to more confusion than clarity. To this end, we give a high-level overview of the key information of each task in Table \ref{tbl:framework_overview}, hoping to serve as a valuable starting point for researchers to optimize their DL-based image-to-image transformation using \emph{MMV\_Im2Im}. The full configuration details are available in human-readable formats in our GitHub repository (https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs).
